Impact of Isotope Fidelity on Fuel Cycle Calculations

### 2016-08-09 paper.tex
update title
correction of Tab label name
fix major issue with non referenced numbers

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
calculation}
\author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }

@@

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

@@

This analysis is focused only on the second strata of EG29, represented by a
single PWR reactor using MOX fuel. After irradiation the uranium and the
plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
the PWR. The separation efficiency is $0.988$. The separated U/Pu (``J1''
stream) is then separated into two sub-stream, one used for new PWR deployment
(``J1\_prime\_storage'' on Fig. \ref{fig:flow}) and the other one for the
production the new batch of MOX fuel (``J1\_second\_storage''). The respective
fraction of those sub-stream are $0.105$ and $0.895$.

@@

\begin{table*}[htb]
  \centering
  \begin{tabular}{llllllllllll}\toprule
    Stream 
    & $^{234}$U   & $^{235}$U   & $^{236}$U   & $^{238}$U   
    & $^{238}$Pu  & $^{239}$Pu  & $^{240}$Pu  & $^{241}$Pu  & $^{242}$Pu 
    & $^{241}$Am  & F.P. \\ \midrule
    E3 [\%]
    & $0.002$   & $0.203$    & $0.083$   & $81.082$
    & $0.0087$  & $17.9764$  & $0.6166$  & $0.0216$  & $0.0007$
    & $0$         & $0$ \\
    J1 [\%]
    & $0$       & $0$        & $0$       & $93.632$
    & $0.1216$  & $2.7058$   & $1.8193$  & $0.7402$  & $0.6833$
    & $0.2978$  & $0$ \\
    \bottomrule
  \end{tabular}
  \caption{Streams compositions in percentage by mass.}
  \label{tab:strem_compo}
\end{table*}

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Impact of Isotope Fidelity on Fuel Cycle Calculations}
\author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }

@@

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{hyperref}

@@

This analysis is focused only on the second strata of EG29, represented by a
single PWR reactor using MOX fuel. After irradiation the uranium and the
plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
the PWR. As no loss are associated to the fabrication process, the separation
efficiency is set at $0.988$, which corresponding to the $1\%$ loss in
separation and the $0.2\%$ during fabrication as specified in \cite{FCDP}).
About $10\%$ of this U/Pu stream (``J1`` stream) is arbitrary set aside in order
to support an hypothetical new PWR deployment (``J1\_prime\_storage), the
remaining $90\%$ is used for the production the new batch of MOX fuel
(``J1\_second\_storage'').

@@

\begin{table*}[htb]
  \centering
  \caption{Streams compositions in percentage by mass.}
  \begin{tabular}{llllllllllll}\toprule
    Stream 
    & $^{234}$U   & $^{235}$U   & $^{236}$U   & $^{238}$U   
    & $^{238}$Pu  & $^{239}$Pu  & $^{240}$Pu  & $^{241}$Pu  & $^{242}$Pu 
    & $^{241}$Am  & F.P. \\ \midrule
    E3 [\%]
    & $0.002$   & $0.203$    & $0.083$   & $81.082$
    & $0.0087$  & $17.9764$  & $0.6166$  & $0.0216$  & $0.0007$
    & $0$         & $0$ \\
    J1 [\%]
    & $0$       & $0$        & $0$       & $93.632$
    & $0.1216$  & $2.7058$   & $1.8193$  & $0.7402$  & $0.6833$
    & $0.2978$  & $0$ \\
    \bottomrule
  \end{tabular}
  \label{tab:stream_compo}
\end{table*}
